### 2011-02-10 paper/results.tex
change

%\acmFig{explore_dim_1}{1}{Fitness mean and standard deviation
%  vs. dimension 1.  The circle is a common point in
%  \figref{explore_dim_1} through \figref{explore_dim_5}}
%\acmFig{explore_dim_2}{1}{Fitness mean and standard deviation
%  vs. dimension 2.  The circle is a common point in
%  \figref{explore_dim_1} through \figref{explore_dim_5}}
%\acmFig{explore_dim_3}{1}{Fitness mean and standard deviation
%  vs. dimension 3.  The circle is a common point in
%  \figref{explore_dim_1} through \figref{explore_dim_5}}
%\acmFig{explore_dim_4}{1}{Fitness mean and standard deviation
%  vs. dimension 4.  The circle is a common point in
%  \figref{explore_dim_1} through \figref{explore_dim_5}}
%\acmFig{explore_dim_5}{1}{Fitness mean and standard deviation
%  vs. dimension 5.  The circle is a common point in
%  \figref{explore_dim_1} through \figref{explore_dim_5}}

\acmFiggggg{explore_dim_1}{explore_dim_2}{explore_dim_3}{explore_dim_4}{explore_dim_5}{1}{.5}{Fitness
  mean and standard deviation vs. dimension 5.  The circle is a common
  point in \figref{explore_dim_1} through \figref{explore_dim_5}}

@@

The maximizing strategies implemented include uniform random hill
climbing, Gaussian random hill climbing, policy gradient descent, and
Nelder-Mead simplex. As a group, these strategies produced results
similar to gaits randomly-generated with the SineModel5 model. None
of these strategies consistently outperformed the others in the three
trials; A different strategy generated the best gait in each
trial. Uniform random hill climbing produced the best gait (11.37 body
lengths/minute) in the first trial, with the next best performing
strategy (Nelder-Mead simplex) resulting in a gait of 8.51 body
lengths/minute. The best gait in the second trial was actually
generated randomly (17.26 body-lengths/minute). Gaussian random hill
climbing, policy gradient descent, and Nelder-Mead simplex all
produced similar best gaits in the second trial, each around 14 body
lengths/minute. In the third trial, Nelder-Mead simplex and Gaussian
random hill climbing significantly outperformed the other maximizing
strategies, resulting in gaits of 14.83 and 13.40 body lengths/minute
respectively. Overall, Nelder-Mead simplex performed the best,
producing an average best gait of 12.32 body lengths/minute. Gaussian
random hill climbing followed, with an average best gait of 10.03 body
lengths/minute.

>>>>

\acmFig{explore_dim_1}{1}{Fitness mean and standard deviation
  vs. dimension 1.  The circle is a common point in
  \figref{explore_dim_1} through \figref{explore_dim_5}}
\acmFig{explore_dim_2}{1}{Fitness mean and standard deviation
  vs. dimension 2.  The circle is a common point in
  \figref{explore_dim_1} through \figref{explore_dim_5}}
\acmFig{explore_dim_3}{1}{Fitness mean and standard deviation
  vs. dimension 3.  The circle is a common point in
  \figref{explore_dim_1} through \figref{explore_dim_5}}
\acmFig{explore_dim_4}{1}{Fitness mean and standard deviation
  vs. dimension 4.  The circle is a common point in
  \figref{explore_dim_1} through \figref{explore_dim_5}}
\acmFig{explore_dim_5}{1}{Fitness mean and standard deviation
  vs. dimension 5.  The circle is a common point in
  \figref{explore_dim_1} through \figref{explore_dim_5}}

@@

The maximizing strategies implemented include uniform random hill
climbing, Gaussian random hill climbing, policy gradient descent, and
Nelder-Mead simplex. As a group, these strategies produced results
similar to or worse than gaits randomly-generated with the SineModel5 model (\figref{std_error}). None
of these strategies consistently outperformed the other maximizing strategies in the three
trials; A different strategy generated the best gait in each
trial. Uniform random hill climbing produced the best gait (11.37 body
lengths/minute) in the first trial, with the next best performing
strategy (Nelder-Mead simplex) resulting in a gait of 8.51 body
lengths/minute. The best gait in the second trial was actually
generated randomly (17.26 body-lengths/minute). Gaussian random hill
climbing, policy gradient descent, and Nelder-Mead simplex all
produced similar best gaits in the second trial, each around 14 body
lengths/minute. In the third trial, Nelder-Mead simplex and Gaussian
random hill climbing significantly outperformed the other maximizing
strategies, resulting in gaits of 14.83 and 13.40 body lengths/minute
respectively. Overall, Nelder-Mead simplex performed the best,
producing an average best gait of 12.32 body lengths/minute. Gaussian
random hill climbing followed, with an average best gait of 10.03 body
lengths/minute.
